Predicting FOMC Actions using ML and NLP

### 2019-04-29 presentation/paper.tex
update

@@

\end{thebibliography}

>>>>

\subsection{Feature Choice}

Based on previous research that applied Naive Bayes to analyzing FOMC transcripts \cite{stanford} ML models performed better with N-grams and performance peaked at tri-grams for Naive Bayes.  In our models, we found that N-grams of greater N saw greater accuracy and lower standard deviation.

@@

\bibitem{stanford} Puri, Indira \emph{USING MACHINE LEARNING TO PREDICT INTEREST RATE CHANGES FROM FEDERAL RESERVE PROCEEDINGS}
\end{thebibliography}
